cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added initial cube projections

>>>>

```{r data-gridcube, echo=TRUE}
gridcube <- gen_gridcube(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(gridcube)
```

```{r gridcube-proj1}
scaled_data <- scale_data_manual(gridcube)

gridcube_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gridcube-proj2}

gridcube_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gridcube-proj3}

gridcube_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-gridcube-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` data."}
#| fig-width: 15
#| fig-height: 5

gridcube_proj1 + gridcube_proj2 + gridcube_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-unifcube, echo=TRUE}
unifcube <- gen_unifcube(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(unifcube)
```

```{r unifcube-proj1}
scaled_data <- scale_data_manual(unifcube)

unifcube_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r unifcube-proj2}

unifcube_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r unifcube-proj3}

unifcube_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-unifcube-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `unifcube` data."}
#| fig-width: 15
#| fig-height: 5

unifcube_proj1 + unifcube_proj2 + unifcube_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-cubehole, echo=TRUE}
cubehole <- gen_cubehole(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(cubehole)
```

```{r cubehole-proj1}
scaled_data <- scale_data_manual(cubehole)

cubehole_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r cubehole-proj2}

cubehole_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r cubehole-proj3}

cubehole_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-cubehole-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cubehole` data."}
#| fig-width: 15
#| fig-height: 5

cubehole_proj1 + cubehole_proj2 + cubehole_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
